Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-14 paper/section_1_intro.tex
Add tilde

\eat{The contextual word
	embeddings provided by these methods have helped establish new
	state-of-the-art
	results on many natural language understanding benchmarks including GLUE
	\cite{Wang2019GLUE}, SuperGLUE \cite{Wang2019SuperGLUEAS}, and SQuAD
	\cite{Rajpurkar2016SQuAD, Rajpurkar2018KnowWY}, even surpassing the human
	baselines in many cases.}

\eat{In parallel to the development of these pre-training methods, many novel
techniques have been proposed to improve training convergence and handle more
diverse data inputs. The most significant contribution is the use of byte-pair
encoding (BPE) \cite{Sennrich2015NeuralMT} to represent a rare word as a
sequence of subword units, thus giving models the ability to handle an open
vocabulary.}

@@

%\sout{
%Most existing captioning systems can only generate a generic description
%of an
%image \cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,
%Karpathy2015DeepVA, Rennie2017SelfCriticalST, Lu2017KnowingWT,
%Anderson2017BottomUpAT, Cornia2019ShowCT}, mainly because these architectures
%cannot handle an open vocabulary and early captioning datasets such as MS COCO
%\cite{Lin2014MicrosoftCC, Chen2015MicrosoftCC} and Flickr30k
%\cite{Young2014FromID} were annotated using only visual cues present in the
%image. More recently, datasets such as TIME \cite{Tariq2017ACE}, BreakingNews
%\cite{Ramisa2016BreakingNewsAA}, and GoodNews \cite{Biten2019GoodNews} include
%real-life captions written by professional journalists. However, existing
%models that are trained on these news datasets still need to rely on either
%extractive methods or templates to insert named entities.}

>>>>

\eat{The contextual word
	embeddings provided by these methods have helped establish new
	state-of-the-art
	results on many natural language understanding benchmarks including GLUE
	\cite{Wang2019GLUE}, SuperGLUE~\cite{Wang2019SuperGLUEAS}, and SQuAD
	\cite{Rajpurkar2016SQuAD, Rajpurkar2018KnowWY}, even surpassing the human
	baselines in many cases.}

\eat{In parallel to the development of these pre-training methods, many novel
techniques have been proposed to improve training convergence and handle more
diverse data inputs. The most significant contribution is the use of byte-pair
encoding (BPE)~\cite{Sennrich2015NeuralMT} to represent a rare word as a
sequence of subword units, thus giving models the ability to handle an open
vocabulary.}

@@

%\sout{
%Most existing captioning systems can only generate a generic description
%of an
%image~\cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,
%Karpathy2015DeepVA, Rennie2017SelfCriticalST, Lu2017KnowingWT,
%Anderson2017BottomUpAT, Cornia2019ShowCT}, mainly because these architectures
%cannot handle an open vocabulary and early captioning datasets such as MS COCO
%\cite{Lin2014MicrosoftCC, Chen2015MicrosoftCC} and Flickr30k
%\cite{Young2014FromID} were annotated using only visual cues present in the
%image. More recently, datasets such as TIME~\cite{Tariq2017ACE}, BreakingNews
%\cite{Ramisa2016BreakingNewsAA}, and GoodNews~\cite{Biten2019GoodNews} include
%real-life captions written by professional journalists. However, existing
%models that are trained on these news datasets still need to rely on either
%extractive methods or templates to insert named entities.}

### 2019-11-14 paper/section_2_literature.tex
Add tilde

A large number of methods exist for generating generic image captions that
describe objects and relationships using only the image as input. Many of these
captioning systems use some combination of a Convolutional Neural Network
encoder and an RNN with a closed
vocabulary as a decoder~\cite{Karpathy2015DeepVA, Donahue2015LongTR,
Vinyals2015ShowAT}.
Attention over image patches was introduced in ``Show, Attend and Tell"
\cite{Xu2015ShowAA}, in which the attention weights are obtained by feeding the
image embeddings and the previous hidden state of the RNN through a multilayer
perception. Many extensions to these models have been proposed such as giving
the model the option to not
attend to any image region~\cite{Lu2017KnowingWT}, using reinforcement learning
to directly optimise for the CIDEr metric~\cite{Rennie2017SelfCriticalST,
Gao2019DeliberateAN}, and using a bottom-up approach to propose a region to
attend to \cite{Anderson2017BottomUpAT}. All of these systems generate
restricted vocabulary generic captions without considering context external to
the image.

A related task which does consider image context is news image captioning,
where the image caption is generated using the article text as context.
One key challenge of news image captioning is generating rare entity names, for
example the names of people who do not make many media appearances. Early
non-neural approaches include
extractive methods that use n-gram models to combine existing phrases
\cite{Feng2013AutomaticCG} or simply retrieving the most representative
sentence \cite{Tariq2017ACE} in the article. The neural network approach taken
by Ramisa \etal
\cite{Ramisa2016BreakingNewsAA} was able to generate entirely new text with an
LSTM decoder that took as input a word2vec representation of the
article concatenated with a CNN representation of the image. Even so this
approach was unable produce names that were not seen during training.

To overcome the limitation of a fixed-size vocabulary caption templates can be
used. This involves first generating a
template sentence with placeholders for named entities, e.g. ``PERSON speaks at
BUILDING in
DATE.''. This template can be generated using an LSTM or other sequence
generation model~\cite{Biten2019GoodNews}. Afterwards, a selection algorithm
picks the best candidate
for each placeholder. For example, Lu \etal \cite{Lu2018EntityAI} built a
knowledge graph
for each combination of entities and select the most likely combination.
Meanwhile, Biten \etal~\cite{Biten2019GoodNews} filled the template by
extracting entities from the sentence in the article which had the highest
cosine similarity to
the template. One key difference between our proposed model and that of
previous approaches\cite{Biten2019GoodNews,Lu2018EntityAI} is that our model can
generate a captions with named entities directly -- without using an
intermediate template.

@@

One tool that has had seen recent successes in many natural language processing
tasks is the transformer neural network.
%\sout{processing, which consist of layers of
%	self-attention and feed-forward connections stacked on top of each other
%	\cite{Vaswani2017AttentionIA}. Transformers have}
Transformers have been show to consistently
outperforming Recurrent Neural Network architectures in language modeling
\cite{Radford2019LanguageMA},
story generation \cite{Fan2018HierarchicalNS}, summarization
\cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.
%\sout{There are theoretical justifications that transformers could be universal
%	approximations of sequence-to-sequence functions
%\cite{Anonymous2020AreTU}.}
Furthermore, transformer based models such as BERT \cite{Devlin2019BERT}, XLM
\cite{Lample2019CrosslingualLM}, XLNet \cite{Yang2019XLNetGA}, RoBERTa
\cite{Liu2019RoBERTaAR}, and ALBERT \cite{Lan2019ALBERT} have been shown to
produce high level text representations suitable for transfer learning.
Furthermore, using byte-pair
encoding (BPE) \cite{Sennrich2015NeuralMT} to represent uncommon words as a
sequence of subword units can enable the transformer function in an open
vocabulary setting.

@@

BPE offers an elegant solution to handling an open vocabulary. To date the only
image captioning work that uses BPE is \cite{Sharma2018ConceptualCA}, but they
did not use it for rare named entities as these were removed from
the captions during pre-processing. In contrast we explicitly examine the use
of BPE for generating rare names and evaluate it in comparison to
template-based methods.

@@

In addition to attending to image patches, some captioning models also attend
to object regions \cite{Wang2019Hierarchical} and visual concepts
\cite{You2016ImageCW,Li2019Boosted,Wang2019Hierarchical}, both of which are
derived from the image itself. When attending to more than one modality, there
are various strategies on how to combine embeddings such as addition,
concatenation, and multivariate residual modules (MRMs)
\cite{Kim2016MultimodalRL}. In our model we use the vector concatenation
strategy and leave investigation of the more complex strategies, such as MMRs,
to future work as they typically only yield minor performance
improvements~\cite{Wang2019Hierarchical}.

>>>>

A large number of methods exist for generating generic image captions that
describe objects and relationships using only the image as input. Many of these
captioning systems use some combination of a Convolutional Neural Network
encoder and an RNN with a closed
vocabulary as a decoder~\cite{Karpathy2015DeepVA, Donahue2015LongTR,
Vinyals2015ShowAT}.
Attention over image patches was introduced in ``Show, Attend and Tell"
\cite{Xu2015ShowAA}, in which the attention weights are obtained by feeding the
image embeddings and the previous hidden state of the RNN through a multilayer
perception. Many extensions to these models have been proposed such as giving
the model the option to not
attend to any image region~\cite{Lu2017KnowingWT}, using reinforcement learning
to directly optimise for the CIDEr metric~\cite{Rennie2017SelfCriticalST,
Gao2019DeliberateAN}, and using a bottom-up approach to propose a region to
attend to~\cite{Anderson2017BottomUpAT}. All of these systems generate
restricted vocabulary generic captions without considering context external to
the image.

A related task which does consider image context is news image captioning,
where the image caption is generated using the article text as context.
One key challenge of news image captioning is generating rare entity names, for
example the names of people who do not make many media appearances. Early
non-neural approaches include
extractive methods that use n-gram models to combine existing phrases
\cite{Feng2013AutomaticCG} or simply retrieving the most representative
sentence~\cite{Tariq2017ACE} in the article. The neural network approach taken
by Ramisa \etal
\cite{Ramisa2016BreakingNewsAA} was able to generate entirely new text with an
LSTM decoder that took as input a word2vec representation of the
article concatenated with a CNN representation of the image. Even so this
approach was unable produce names that were not seen during training.

To overcome the limitation of a fixed-size vocabulary caption templates can be
used. This involves first generating a
template sentence with placeholders for named entities, e.g. ``PERSON speaks at
BUILDING in
DATE.''. This template can be generated using an LSTM or other sequence
generation model~\cite{Biten2019GoodNews}. Afterwards, a selection algorithm
picks the best candidate
for each placeholder. For example, Lu \etal~\cite{Lu2018EntityAI} built a
knowledge graph
for each combination of entities and select the most likely combination.
Meanwhile, Biten \etal~\cite{Biten2019GoodNews} filled the template by
extracting entities from the sentence in the article which had the highest
cosine similarity to
the template. One key difference between our proposed model and that of
previous approaches\cite{Biten2019GoodNews,Lu2018EntityAI} is that our model can
generate a captions with named entities directly -- without using an
intermediate template.

@@

One tool that has had seen recent successes in many natural language processing
tasks is the transformer neural network.
%\sout{processing, which consist of layers of
%	self-attention and feed-forward connections stacked on top of each other
%	\cite{Vaswani2017AttentionIA}. Transformers have}
Transformers have been show to consistently
outperforming Recurrent Neural Network architectures in language modeling
\cite{Radford2019LanguageMA},
story generation~\cite{Fan2018HierarchicalNS}, summarization
\cite{Subramanian2019OnEA}, and machine translation~\cite{Bojar2018Findings}.
%\sout{There are theoretical justifications that transformers could be universal
%	approximations of sequence-to-sequence functions
%\cite{Anonymous2020AreTU}.}
Furthermore, transformer based models such as BERT~\cite{Devlin2019BERT}, XLM
\cite{Lample2019CrosslingualLM}, XLNet~\cite{Yang2019XLNetGA}, RoBERTa
\cite{Liu2019RoBERTaAR}, and ALBERT~\cite{Lan2019ALBERT} have been shown to
produce high level text representations suitable for transfer learning.
Furthermore, using byte-pair
encoding (BPE)~\cite{Sennrich2015NeuralMT} to represent uncommon words as a
sequence of subword units can enable the transformer function in an open
vocabulary setting.

@@

BPE offers an elegant solution to handling an open vocabulary. To date the only
image captioning work that uses BPE is~\cite{Sharma2018ConceptualCA}, but they
did not use it for rare named entities as these were removed from
the captions during pre-processing. In contrast we explicitly examine the use
of BPE for generating rare names and evaluate it in comparison to
template-based methods.

@@

In addition to attending to image patches, some captioning models also attend
to object regions~\cite{Wang2019Hierarchical} and visual concepts
\cite{You2016ImageCW,Li2019Boosted,Wang2019Hierarchical}, both of which are
derived from the image itself. When attending to more than one modality, there
are various strategies on how to combine embeddings such as addition,
concatenation, and multivariate residual modules (MRMs)
\cite{Kim2016MultimodalRL}. In our model we use the vector concatenation
strategy and leave investigation of the more complex strategies, such as MMRs,
to future work as they typically only yield minor performance
improvements~\cite{Wang2019Hierarchical}.

### 2019-11-14 paper/section_3_model.tex
Add tilde

We use MTCNN~\cite{Zhang2016JointFD} to detect face bounding boxes in the
image. We then select the largest four faces since the majority of captions
have at most four personal names (see \ref{ssec:nytimes800k}). A vector
representation of each face is obtained by passing the bounding boxes to
FaceNet~\cite{Schroff2015FaceNetAU}, which was pre-trained on the VGGFace2
dataset~\cite{Cao2017VGGFace2AD}. The resulting set of face vectors for each
image is $\bx_{F} = \{\bx_{Fi} \in \mathbb{R}^{512}\}_{i=1}^4$.

@@

\eat{We then select the top $M$ faces and feed them through a
FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bx_{F} =
\{\bx_{F,i} \in \mathbb{R}^{512}\}_{i=0}^M$.}

@@

To encode the article text we use RoBERTa~\cite{Liu2019RoBERTaAR} which is a
recent improvement over the popular BERT~\cite{Devlin2019BERT} model.
RoBERTa is a language representation model that provides pretrained contextual
embeddings for text. It consists of 24 layers of bidirectional transformer
blocks.
% It is a more carefully trained BERT \cite{Devlin2019BERT} model.

Unlike GloVe \cite{Pennington2014Glove} and word2vec
\cite{Mikolov2013DistributedRO} embeddings, where each word has exactly one
representation, the bidirectionality and the attention mechanism in the
transformer allow a word to have different vector representations depending on
the surrounding context.

The largest GloVe model has a vocabulary size of 1.2 million. Although this is
large, many rare names will still get mapped to the unknown token. In contrast,
RoBERTa uses BPE \cite{Sennrich2015NeuralMT,Radford2019LanguageMA} which can
encode any word that can be written in Unicode characters.

@@

The decoder is a function that estimates $p(y_t)$, the probability of the $t$th
token in the caption, conditional on the past $\by_{<t}$ and the context
embeddings $\bX_I$, $\bX_T$, and $\bX_F$:
\begin{IEEEeqnarray*}{lCl}
   p(y_t) &=& \mathbb{P}(Y_t = y_t \mid \by_{<t}, \bX_I, \bX_T, \bX_F)
\end{IEEEeqnarray*}
In our architecture, the decoder consists of four transformer blocks. In each
block, the conditioning on past tokens is computed using dynamic convolutions
\cite{Wu2018PayLA}, and the conditioning on the contexts is computed using
multi-head attention \cite{Vaswani2017AttentionIA}.

@@

Instead of using the standard self-attention module as in current
state-of-the-art GPT-2 decoder \cite{Radford2019LanguageMA}, we find that
dynamic convolutions \cite{Wu2018PayLA} are more efficient to train. Suppose
when decoding the $t$th token, we have at the $\ell$th block the input
$\bz_{\ell t} \in \mathbb{R}^{1024}$. If $\ell = 0$, then $\bz_{0t}$ is the
embedding of the previous token. Otherwise it is the output from the previous
transformer block. Given kernel size $K$ and 16 attention heads, for each head
$h \in \{1, 2, ..., 16\}$, we first project the current and last $K-1$ steps
using a feedforward layer:
\begin{IEEEeqnarray*}{lCl}
   \bz_{\ell,h,t-j}' &=& \text{GLU}(\bW_{z\ell h} \, \bz_{\ell,t-j} + \bb_{z\ell h})
\end{IEEEeqnarray*}
where $j \in \{0,1,...,K-1\}$, GLU is the gated linear unit activation
function~\cite{Dauphin2017GLU}, and $\bz_{\ell,h,t-j}' \in \mathbb{R}^{64}$.
The output of each head's dynamic convolution is the weighted sum of these
projected values:
\begin{IEEEeqnarray*}{lCl}
   \tz_{\ell h t} &=& \sum_{j=0}^{K-1} \gamma_{\ell hj} \, \bz_{\ell, h, t-j}'
\end{IEEEeqnarray*}
where the weight $\gamma_{\ell hj}$ is a linear projection of the input,
followed by a softmax over the kernel window:
\begin{IEEEeqnarray*}{lCl}
   \gamma_{\ell hj} &=& \text{Softmax} \left( \bw^T_{\gamma \ell h} \,
      \bz_{\ell,h,t-j} \right)
\end{IEEEeqnarray*}
The overall output is the concatenation of all the head outputs, followed by
a feedforward with a residual connection and layer normalization:
\begin{IEEEeqnarray*}{lCl}
   \tz_{\ell t} &=& [ \tz_{\ell 1 t}, \tz_{\ell 2 t},..., \tz_{\ell 16 t} ] \\
   \bd_{\ell t} &=& \text{LayerNorm}\left( \bz_{\ell t} +
             \bW_{\tz \ell} \, \tz_{\ell t} + \bb_{\tz \ell} \right)
\end{IEEEeqnarray*}
Note that given kernel size $K$, we can attend to the current time step and the
last $K-1$ steps. Following closely to \cite{Wu2018PayLA}, our decoder has 4
transformer blocks with kernel sizes 3, 7, 15, and 31, respectively. Thus the
final block output will have collected information from the last 51 tokens.

@@

\subsubsection{Mixing RoBERTa layers}
RoBERTa consists of 24 layers of bidirectional transformer blocks. Given an
input of length $S$, the pretrained RoBERTa encoder will return 25 sequences of
embeddings, $\bG = \{\bg_{\ell i} \in \mathbb{R}^{2048} : i \in \{1, 2,...,
49\}, \ell \in \{ 0, 1,..., 24 \}\}$. This includes the initial
uncontextualized embeddings and the output of each of the 24 layers. Inspired
by Tenney \etal \cite{Tenney2019BertRT}, who showed that different layers in
BERT represent different steps in the traditional NLP pipeline, we take a
weighted sum across all layers to obtain the article embedding $\bx_{Ti}$:
\begin{IEEEeqnarray*}{lCl}
   \bx_{Ti} &=& \sum_{\ell=0}^{24} \alpha_\ell \, \bg_{\ell i}
\end{IEEEeqnarray*}
where  $\alpha_\ell$ are learnable weights.

@@

Inspired by pointer-generator networks \cite{See2017GetTT}, we introduce a
copying mechanism using multi-head attention. We use the final layer output
$\bz_{5t}$ and the article embeddings $\bX_T$ as inputs to the multi-head
attention module. Unlike \ref{ssection:attn}, we only need to compute the
softmax weights $\lambda_i$ (and not the weighted sum of the values). We
interpret each $\lambda_i$ as the probability of copying $i$th token in the
article.

@@

The decoder BPE vocabulary size is 50265. To make training more efficient, we
use adaptive softmax \cite{Grave2016EfficientSA} and divide the vocabulary into
three clusters: 5K, 15K, and 25K. We tie the adaptive weights and we share the
decoder input and output embeddings. We use sinusoidal positional encoding
\cite{Vaswani2017AttentionIA} to represent the position of each token.

>>>>

We use MTCNN~\cite{Zhang2016JointFD} to detect face bounding boxes in the
image. We then select the largest four faces since the majority of captions
have at most four personal names (see~\ref{ssec:nytimes800k}). A vector
representation of each face is obtained by passing the bounding boxes to
FaceNet~\cite{Schroff2015FaceNetAU}, which was pre-trained on the VGGFace2
dataset~\cite{Cao2017VGGFace2AD}. The resulting set of face vectors for each
image is $\bx_{F} = \{\bx_{Fi} \in \mathbb{R}^{512}\}_{i=1}^4$.

@@

\eat{We then select the top $M$ faces and feed them through a
FaceNet model~\cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bx_{F} =
\{\bx_{F,i} \in \mathbb{R}^{512}\}_{i=0}^M$.}

@@

To encode the article text we use RoBERTa~\cite{Liu2019RoBERTaAR} which is a
recent improvement over the popular BERT~\cite{Devlin2019BERT} model.
RoBERTa is a language representation model that provides pretrained contextual
embeddings for text. It consists of 24 layers of bidirectional transformer
blocks.
% It is a more carefully trained BERT~\cite{Devlin2019BERT} model.

Unlike GloVe~\cite{Pennington2014Glove} and word2vec
\cite{Mikolov2013DistributedRO} embeddings, where each word has exactly one
representation, the bidirectionality and the attention mechanism in the
transformer allow a word to have different vector representations depending on
the surrounding context.

The largest GloVe model has a vocabulary size of 1.2 million. Although this is
large, many rare names will still get mapped to the unknown token. In contrast,
RoBERTa uses BPE~\cite{Sennrich2015NeuralMT,Radford2019LanguageMA} which can
encode any word that can be written in Unicode characters.

@@

The decoder is a function that estimates $p(y_t)$, the probability of the $t$th
token in the caption, conditional on the past $\by_{<t}$ and the context
embeddings $\bX_I$, $\bX_T$, and $\bX_F$:
\begin{IEEEeqnarray*}{lCl}
   p(y_t) &=& \mathbb{P}(Y_t = y_t \mid \by_{<t}, \bX_I, \bX_T, \bX_F)
\end{IEEEeqnarray*}
In our architecture, the decoder consists of four transformer blocks. In each
block, the conditioning on past tokens is computed using dynamic convolutions
\cite{Wu2018PayLA}, and the conditioning on the contexts is computed using
multi-head attention~\cite{Vaswani2017AttentionIA}.

@@

Instead of using the standard self-attention module as in current
state-of-the-art GPT-2 decoder~\cite{Radford2019LanguageMA}, we find that
dynamic convolutions~\cite{Wu2018PayLA} are more efficient to train. Suppose
when decoding the $t$th token, we have at the $\ell$th block the input
$\bz_{\ell t} \in \mathbb{R}^{1024}$. If $\ell = 0$, then $\bz_{0t}$ is the
embedding of the previous token. Otherwise it is the output from the previous
transformer block. Given kernel size $K$ and 16 attention heads, for each head
$h \in \{1, 2, ..., 16\}$, we first project the current and last $K-1$ steps
using a feedforward layer:
\begin{IEEEeqnarray*}{lCl}
   \bz_{\ell,h,t-j}' &=& \text{GLU}(\bW_{z\ell h} \, \bz_{\ell,t-j} + \bb_{z\ell h})
\end{IEEEeqnarray*}
where $j \in \{0,1,...,K-1\}$, GLU is the gated linear unit activation
function~\cite{Dauphin2017GLU}, and $\bz_{\ell,h,t-j}' \in \mathbb{R}^{64}$.
The output of each head's dynamic convolution is the weighted sum of these
projected values:
\begin{IEEEeqnarray*}{lCl}
   \tz_{\ell h t} &=& \sum_{j=0}^{K-1} \gamma_{\ell hj} \, \bz_{\ell, h, t-j}'
\end{IEEEeqnarray*}
where the weight $\gamma_{\ell hj}$ is a linear projection of the input,
followed by a softmax over the kernel window:
\begin{IEEEeqnarray*}{lCl}
   \gamma_{\ell hj} &=& \text{Softmax} \left( \bw^T_{\gamma \ell h} \,
      \bz_{\ell,h,t-j} \right)
\end{IEEEeqnarray*}
The overall output is the concatenation of all the head outputs, followed by
a feedforward with a residual connection and layer normalization:
\begin{IEEEeqnarray*}{lCl}
   \tz_{\ell t} &=& [ \tz_{\ell 1 t}, \tz_{\ell 2 t},..., \tz_{\ell 16 t} ] \\
   \bd_{\ell t} &=& \text{LayerNorm}\left( \bz_{\ell t} +
             \bW_{\tz \ell} \, \tz_{\ell t} + \bb_{\tz \ell} \right)
\end{IEEEeqnarray*}
Note that given kernel size $K$, we can attend to the current time step and the
last $K-1$ steps. Following closely to~\cite{Wu2018PayLA}, our decoder has 4
transformer blocks with kernel sizes 3, 7, 15, and 31, respectively. Thus the
final block output will have collected information from the last 51 tokens.

@@

\subsubsection{Mixing RoBERTa layers}
RoBERTa consists of 24 layers of bidirectional transformer blocks. Given an
input of length $S$, the pretrained RoBERTa encoder will return 25 sequences of
embeddings, $\bG = \{\bg_{\ell i} \in \mathbb{R}^{2048} : i \in \{1, 2,...,
49\}, \ell \in \{ 0, 1,..., 24 \}\}$. This includes the initial
uncontextualized embeddings and the output of each of the 24 layers. Inspired
by Tenney \etal~\cite{Tenney2019BertRT}, who showed that different layers in
BERT represent different steps in the traditional NLP pipeline, we take a
weighted sum across all layers to obtain the article embedding $\bx_{Ti}$:
\begin{IEEEeqnarray*}{lCl}
   \bx_{Ti} &=& \sum_{\ell=0}^{24} \alpha_\ell \, \bg_{\ell i}
\end{IEEEeqnarray*}
where  $\alpha_\ell$ are learnable weights.

@@

Inspired by pointer-generator networks~\cite{See2017GetTT}, we introduce a
copying mechanism using multi-head attention. We use the final layer output
$\bz_{5t}$ and the article embeddings $\bX_T$ as inputs to the multi-head
attention module. Unlike~\ref{ssection:attn}, we only need to compute the
softmax weights $\lambda_i$ (and not the weighted sum of the values). We
interpret each $\lambda_i$ as the probability of copying $i$th token in the
article.

@@

The decoder BPE vocabulary size is 50265. To make training more efficient, we
use adaptive softmax~\cite{Grave2016EfficientSA} and divide the vocabulary into
three clusters: 5K, 15K, and 25K. We tie the adaptive weights and we share the
decoder input and output embeddings. We use sinusoidal positional encoding
\cite{Vaswani2017AttentionIA} to represent the position of each token.

### 2019-11-14 paper/section_4_datasets.tex
Work on dynamic convolution section
Add tilde

\subsection{NYTimes800k}

@@

Table \ref{tab:datasets} presents a comparison between GoodNews and
NYTimes800k. NYTimes800k exhibits several advantages:

@@

Entities play an important role in the dataset, with 97\% of captions
containing at least one named entity. As shown in Figure \ref{fig:entities},
the most popular entity type are names of people, comprising a third of all
named entities. Furthermore, 71\% of training images contain at least one face
and 68\% of training captions mention at least one persons name. Figure
\ref{fig:faces} provides a further breakdown of the co-occurrence of faces and
personal names. One important observation is that the majority of captions
contain at most four names.

@@

We split the training, validation, and test sets according to time, as shown in
Table \ref{tab:splits}. For example, the test set consists of all captions and
articles in the final three months of the collection period, from June to
August 2019. This has two advantages over the random split used in GoodNews.
Firstly, it prevents captions in the training and test sets from sharing the
same context article, which allows us to evaluate how well the model can
generalize to new articles. Secondly, due of the shift in the coverage of news
over time, there
will be events and people in the test data that have never been covered by the
news
before. In particular, out of the 100K proper nouns in the test captions, 4\%
never appear in any training captions. Half of these also never appear in any
training article. Thus splitting by time allows us study how well the model can
generate rare names.

>>>>

\subsection{NYTimes800k}
\label{ssec:nytimes800k}

@@

Table~\ref{tab:datasets} presents a comparison between GoodNews and
NYTimes800k. NYTimes800k exhibits several advantages:

@@

Entities play an important role in the dataset, with 97\% of captions
containing at least one named entity. As shown in Figure~\ref{fig:entities},
the most popular entity type are names of people, comprising a third of all
named entities. Furthermore, 71\% of training images contain at least one face
and 68\% of training captions mention at least one persons name. Figure
\ref{fig:faces} provides a further breakdown of the co-occurrence of faces and
personal names. One important observation is that the majority of captions
contain at most four names.

@@

We split the training, validation, and test sets according to time, as shown in
Table~\ref{tab:splits}. For example, the test set consists of all captions and
articles in the final three months of the collection period, from June to
August 2019. This has two advantages over the random split used in GoodNews.
Firstly, it prevents captions in the training and test sets from sharing the
same context article, which allows us to evaluate how well the model can
generalize to new articles. Secondly, due of the shift in the coverage of news
over time, there
will be events and people in the test data that have never been covered by the
news
before. In particular, out of the 100K proper nouns in the test captions, 4\%
never appear in any training captions. Half of these also never appear in any
training article. Thus splitting by time allows us study how well the model can
generate rare names.

### 2019-11-14 paper/section_5_experiments.tex
Add tilde

In all experiments, we use Adam \cite{Kingma2015Adam} with the weight decay fix
\cite{Loshchilov2018DecoupledWD} to optimize the models. We use the following
parameters: $\beta_1 = 0.9, \beta_2 = 0.98, \epsilon = 10^{-6}$, and a weight
decay of $10^{-5}$. We clip the gradient norm at 0.1. All models see the same
number of training examples, which is 6.6 million. This is equivalent to 16
epochs through GoodNews and 9 epochs through NYTimes800k. We warm up the
learning rate in the first 5\% of the training steps to $10^{-4}$, and decays
it linearly afterwards. Training is done with mixed precision to reduce the
memory footprint. The full model takes 5 days to train on one Titan V GPU.

As shown in Table \ref{tab:models}, all of our baselines are designed to have
roughly the same number of trainable parameters. This allows us to attribute
improvement to the individual model components rather than to simply having a
bigger model.

The training pipeline is written in PyTorch \cite{Paszke2017Automatic} using
the AllenNLP framework \cite{Gardner2017AllenNLP}. The RoBERTa model and
dynamic convolution code are adapted from fairseq \cite{Ott2019Fairseq}.

@@

Table \ref{tab:results} shows the BLEU \cite{Papineni2002Bleu}, ROUGE
\cite{Lin2004ROUGE}, METEOR \cite{Denkowski2014Meteor}, and CIDEr
\cite{Vedantam2015CIDEr} metrics on GoodNews and NYTimes800k. We show two best
results from the previous state-of-the-art \cite{Biten2019GoodNews}. Note that
the numbers reported here are slightly different from the original paper since
we had to remove a few samples from the test set where the image is no longer
available. \cite{Biten2019GoodNews} also did some post-processing on the
ground-truth captions such as removing contractions and non-ASCII characters,
both of which we did not do. Despite these differences, the final metrics
are the same if rounded to the nearest whole number.

There is a strong correlation between of all these metrics, and in general, we
mainly look at CIDEr since it uses Term Frequency Inverse Document Frequency
(TF-IDF) to put more importance on less common words such as entity names.
Table \ref{tab:names} shows the recall and precision of the named entities,
personal names, and rare proper nouns.

@@

\begin{itemize}
   \item Our baseline LSTM model with GloVe embeddings yields competitive
   results to previous the state-of-the-art \cite{Biten2019GoodNews}. This
   means that BPE offers a viable alternative to template-based methods.

@@

Table \ref{tab:names} also looks at the quality of the generated captions. We
look at three metrics: caption length, type-token ratio (TTR), and Flesch
reading ease. TTR is the ratio of the number of unique words to the total
number of words in a caption. The Flesch reading ease takes into account the
number of words and syllables and produces a score between 0 and 100, where
higher means being easier to read.

>>>>

In all experiments, we use Adam~\cite{Kingma2015Adam} with the weight decay fix
\cite{Loshchilov2018DecoupledWD} to optimize the models. We use the following
parameters: $\beta_1 = 0.9, \beta_2 = 0.98, \epsilon = 10^{-6}$, and a weight
decay of $10^{-5}$. We clip the gradient norm at 0.1. All models see the same
number of training examples, which is 6.6 million. This is equivalent to 16
epochs through GoodNews and 9 epochs through NYTimes800k. We warm up the
learning rate in the first 5\% of the training steps to $10^{-4}$, and decays
it linearly afterwards. Training is done with mixed precision to reduce the
memory footprint. The full model takes 5 days to train on one Titan V GPU.

As shown in Table~\ref{tab:models}, all of our baselines are designed to have
roughly the same number of trainable parameters. This allows us to attribute
improvement to the individual model components rather than to simply having a
bigger model.

The training pipeline is written in PyTorch~\cite{Paszke2017Automatic} using
the AllenNLP framework~\cite{Gardner2017AllenNLP}. The RoBERTa model and
dynamic convolution code are adapted from fairseq~\cite{Ott2019Fairseq}.

@@

Table~\ref{tab:results} shows the BLEU~\cite{Papineni2002Bleu}, ROUGE
\cite{Lin2004ROUGE}, METEOR~\cite{Denkowski2014Meteor}, and CIDEr
\cite{Vedantam2015CIDEr} metrics on GoodNews and NYTimes800k. We show two best
results from the previous state-of-the-art~\cite{Biten2019GoodNews}. Note that
the numbers reported here are slightly different from the original paper since
we had to remove a few samples from the test set where the image is no longer
available.~\cite{Biten2019GoodNews} also did some post-processing on the
ground-truth captions such as removing contractions and non-ASCII characters,
both of which we did not do. Despite these differences, the final metrics
are the same if rounded to the nearest whole number.

There is a strong correlation between of all these metrics, and in general, we
mainly look at CIDEr since it uses Term Frequency Inverse Document Frequency
(TF-IDF) to put more importance on less common words such as entity names.
Table~\ref{tab:names} shows the recall and precision of the named entities,
personal names, and rare proper nouns.

@@

\begin{itemize}
   \item Our baseline LSTM model with GloVe embeddings yields competitive
   results to previous the state-of-the-art~\cite{Biten2019GoodNews}. This
   means that BPE offers a viable alternative to template-based methods.

@@

Table~\ref{tab:names} also looks at the quality of the generated captions. We
look at three metrics: caption length, type-token ratio (TTR), and Flesch
reading ease. TTR is the ratio of the number of unique words to the total
number of words in a caption. The Flesch reading ease takes into account the
number of words and syllables and produces a score between 0 and 100, where
higher means being easier to read.
